---
title: "Retrieving & Merging Data"
author: "Bas Machielsen"
date: "3/1/2021"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Suppose you want have retrieved the ISIN-numbers of a number of companies on which you want to do research. How do you look for those specific companies in Bureau van Dijk/Orbis?

You effectuate a search with:
  - Identifiers
  - Stock and securities number
    - You paste the ISIN numbers in there
    
How do you look for those specific companies in WRDS?
    
### Example

Here is the Excel file on the basis of which you want to retrieve the data (note that I clean the Excel file to make it nicely visible in R): 

```{r excel, message = FALSE, warning = FALSE}
library(readxl); library(tidyverse)

data <- readxl::read_xls("HDAX_ICR.20140131.xls", 
                 sheet = 2) %>%
  janitor::remove_empty() %>%
  janitor::row_to_names(1) %>%
  select(1:7) 

data %>%
  head()


data <- data %>%
  janitor::clean_names() %>%
  select(trading_symbol, instrument, isin) %>%
  distinct()
```

Then, I take the ISIN numbers (in the ISIN column) and go to Bureau van Dijk/Orbis and search for:

- Identifiers
  - Stock and securities number
  - Paste all the ISIN numbers in there
  - Alternatively, you can write the ISIN column to a text file and upload the text file to Orbis:
  
```{r upl to text file}
data %>%
  janitor::clean_names() %>%
  select(isin) %>%
  write_delim("isin_nos.txt",
              col_names = FALSE)
  
```

Note that the argument `col_names = FALSE` has to be included, because databases will not take the first line into account as a column name, but rather, as something to be looked for. It will therefore produce an error if you include it. 

- Orbis will then let you know how many of the ISIN's have been found, and how many haven't been found. 

After having looked up the _companies_ you want to find, you can look up the _variables_. To proceed to that stage, click **View results**. Then, suppose you want to look for the total assets of these companies, as well as for the names of the directors. 

You go to: 

  - Add/Remove Columns
  - Identifiers
  - Add ISIN, Tickers (So that you can find data on these companies in _every_ database, not only BvD/Orbis)

Then, go to:
  - Directors & Managers
  - Other personal information
  - Select Name & Last Name
  - Possibly (but not done here), you can select Date of Installment, Date of Resignation

Then, export the file to .xlsx (or any other extension you like). We can import these data in R now. It is important to run `tidyr::fill()` to fill the rows with their preceding values to do some data cleaning and aggregation later on. `fill()` takes on as arguments the columns that you want to apply this operation on. 

```{r import data}

directors <- read_xlsx("directors.xlsx") %>%
  janitor::clean_names() %>%
  select(-1) %>%
  tidyr::fill(c(1:6))

directors %>%
  head()

```

Now, let's find some information about Bundestag members from Wikipedia:

```{r bundestag, message = FALSE, warning = FALSE}
library(rvest)

bundestag <- read_html("https://en.wikipedia.org/wiki/List_of_members_of_the_17th_Bundestag") %>%
  html_nodes("table.wikitable:nth-child(8)") %>%
  html_table(fill = TRUE) %>%
  purrr::reduce(as.data.frame)


bundestag %>%
  head()
```

Nice, but let's select only the names, and let's put it in the right order:

```{r rightorder}

bundestag <- bundestag %>%
  janitor::clean_names() %>%
  select(name) %>%
  separate(name, into = c("last", "first"), sep = ",") %>%
  mutate(first_last = paste(first, last)) %>%
  select(first_last)

bundestag %>%
  head()

```


Let us now count matches between `directors` and `bundestag`:

```{r matches dir bund, message = FALSE, warning = FALSE}

library(stringdist)

directors <- directors %>%
  mutate(first_last = paste(first_name, last_name)) 
```

First, I paste the first and last name of the directors, so as to match with the first and last names of the Bundestag members, which I put into the same format.

Secondly, I use the `amatch` function from the stringdist package to find whether the name of the director matches the name of a bundestag member. Then, I apply the `if_else` function on the outcome of that calculation. If the outcome of the calculation (which gives me a number, the position of the match in the `bundestag` data.farme) is different from 0, then, count it as a match ("yes"). Otherwise, no match ("no"). 

```{r match dir sec}
directors <- directors %>%
  mutate(inpolitics = if_else(stringdist::amatch(first_last, bundestag$first_last, maxDist = 3) != 0,
                         "yes", 
                         "no")
  )
                         

directors %>%
  arrange(inpolitics)
```

Now, finally, let's merge this dataset on political connections with the data on companies, `data`, on the basis of ISIN. I understand this looks difficult, but what I am doing is this:

1. I group the directors data frame according to ISIN. Now the data.frame consist of virtual 'mini data.frames', each one for each ISIN number. Then, I only select a certain name _once_ per company. Then, I want them to summarize the amount of occurrences of "yes' in the inpolitics variable, i.e., the matches! Then, finally, the `summarize` function makes sure I get the group-variable back. 

```{r finmerge}

no_of_pol_con_per_firm <- directors %>%
  group_by(isin) %>%
  distinct(first_last, .keep_all = TRUE) %>%
  summarize(howmany = sum(inpolitics == "yes",
                          na.rm = TRUE)
            )

no_of_pol_con_per_firm %>%
  ungroup() %>%
  arrange(desc(howmany))
```

Now, we can merge this with `data`, the data.frame we started with:

```{r finmerge2}
merged_data <- left_join(data, no_of_pol_con_per_firm, 
          by = c("isin" = "isin"))


head(merged_data) 
```
  
  
And we can chose to further clean it, because the ISIN's change over time: 


```{r finalclean}
final_data <- merged_data %>%
  group_by(instrument) %>%
  summarize(howmany = sum(howmany, na.rm = TRUE))
```

A quick visualization:

```{r geom}
final_data %>%
  ggplot(aes(x = howmany)) + geom_bar() + 
  xlab("How many political connections?") +
  ylab("Frequency (no. of companies)")
```

### Additional information in WRDS

Remember, that in data:

```{r}
head(data)
```

We also have Isin's, and tickers. We can use that information to find more data about these companies on WRDS if we want to!

## Conclusion

This file showed how to find political connections in a sample of German companies. More nuanced analyses would take into account also the dynamic nature of political connections, and beware of very common names. 

